\bf Adapting the Chumbley Score to match striae on Land Engraved Areas of bullets

### 2018-08-19 doc/Response.Rmd

I'm also confused how the FP rate for Hare CNMS is 6.26% whereas all other FP are 6.25% This seems to likely be a typo. 6.25% imply close to 10,000 comparisons which I don't think the datasets have. I could be wrong but I wanted to point out this potential typo that should be checked.

*Thank you for spotting the typo. With respect to the sample size, the data set being used by \cite{aoas}. has about 10384 land-to-land comparisons and the error rates being reported here are computed from Receiver operating characteristic (ROC) curves. We decided to report False Negative error rates for a fixed value of False Positives (FP) = 6.25% to make them comparable to the observed values in Figure 10 (bottom right)*

The authors describe the two methods of 'failure' for the method (Sec 2.3). I agree with the authors statement that this failure 'should' only happen for non-matches. It could also happen for matches if the optimal profiles are incorrect. That is, if there are two possible optimal match pairs (with very similar correlation scores), where the top scoring pair is incorrect but the second best scoring pair is correct. I'm not sure how often that happens. Overall, I would think that failing for non-matches would be ok. It's not clear that the described failures are the biggest cause of performance hits but improving the algorithm to handle these failures seems reasonable.

*You are right, a failure might occur for a match if the initial optimization fails. The new method is still susceptible to that. It would be interesting to further investigate this problem in the future. We have made a note of that in the conclusions.*

@@

The following sections list specific points that should be addressed before acceptance. They are grouped into clarification/grammar/preciseness, minor, and major revisions.

Some examples of clarification / grammar / preciseness issues:

- p3 "confocal microscopy allow * to measure 3D surfaces in a high-resolution digital form"  * should be "one"?
- p3 "Digitized images of 3D surfaces of form the data basis* of statistical analysis" Awkward phrasing.
- p3 "Faden et al and Chumbley et al have been analyzing screwdriver marks" perhaps change to "have analyzed" because the work is completed and published.
- p9 Seems to be a broken latex figure reference around line 28/29.
These are not all the issues of this type, we encourage the authors to review the manuscript carefully clean issues like the above.

*Thank you for pointing out these issues. We have fixed those accordingly.*

@@

Minor edits should be made to accuracy and clarity:

- p3 "Methods for matching marks for a variety of tools" should be changed to "Methods for matching striated marks for a variety of tools". This is an important point in that it helps make clear that the authors are studying and comparing striated toolmarks and not impressed toolmarks. I would also propose that the authors make this distinction earlier in the introduction.

*We have added emphasis on striae as opposed to impressed toolmarks. *

- p3 "Analysis of these digitized markings require the use of statistical methods". Analysis does not *require* statistical methods. Useful information regarding common origin can be obtained from non-statistical methods. This being said, statistical methods are of course great and we should be working towards them. Authors could change to analysis "benefits from the use of statistical methods" or something similar.
- p14 how are the false negative and false positive rates computed?

*We have added two paragraphs on the Chumbley Score test for clarification: the first paragraph expicitly states the hypotheses involved, the second defines error rates.*

@@

- Eq 1 uses a variable i, which is defined above as having the values of 1 or 2. I therefore don't understand how i<0 as written in Eq 1. This should be improved. Possibly this is a sloppy reuse of variables?

*thank you for pointing this out - we accidentally changed notations. this is fixed now. Index k=1,2 refers to the two different signatures, index i in Z refers to window locations.*

- How are the original profiles (eg. Figure 2 Left) identified from the 3D surface (eg. Figure 1 Top). That is, does the user simply draw a line from one end of the LEA to the other? How is the original 3D surface resampled to the 1d profile? This is very important because if you 'cut' the 3D profile the wrong way (at the wrong angle) then you will dilate or compress the extracted profile. This needs a lot more description.

*We followed the \cite{aoas} paper in extracting the profiles from scans. We have expanded on the discussion at the begining of section titled "Scans for land engraved areas" in the paper.*

@@

- Section 2.4 is not clearly written. I'm not confident that I understand their new method. This section should be rewritten to explain what the authors are doing. My guess is that rather than taking windows in integer number of steps away from the optimal position matching a left shift on one profile with a right shift on the other, the authors simply walk from the right-end to the left-end of one profile and from the left-end to the right-end of the other profile being careful to not compare same shift windows. Note that my description is not clear either as this is a tricky thing to put into words, but is something the authors need to do.

*Thank you for poining this out, you are right in your understanding of the method. We have changed figure 5 for clarification and expanded our discussion, which hopefully makes it easier to understand the method.*

@@

- The results presented on page 14 list the correct identification of "same-source and difference-source toolmarks of 93.5 to 94.1%". Does this mean the true positives are 93.5% and the true negatives are 94.1%? I don't think so because the next sentence lists the false negative rate of between 0.28 and 0.36. The authors need to explicitly list the true positive rate and the true negative rate. These must be separate because there are many more true negatives than true positives in any matching dataset. That means that an algorithm that always predicts "different source" would be correct most of the time. In fact, for the author's dataset the "always predict different" algorithm would be correct approximately 94% of the time (35 bullets where each has appx 2 matches). The lack of a true positive rate and true negative rate is is a major point that must be corrected. To be clear, the true positive rate, true negative rate, false positive rate, and false negative rate should all be reported for the first dataset, perhaps added to Table 3 or another table like Table 3.

*Thank you for bringing this to our notice. We have indluded a paragraph with a definition of error rates, and switched to a table to show the results as suggested below.*

- The true positive rate, true negative rate, false positive rate, and false negative rate should also be presented for the second dataset (Hamby 44 scans, Sec 3.5). The authors do present AUC and EER curves but these are less informative and can often be used to hide weaker performing models.
- The results should all be listed as either fractions or all as percent (which is preferred) and not mix them.

*We have changed the reporting to error percentages.*

- p21 the authors state "this kind of assessment is only feasible in the setting of a large study, such as the one we presented".  I strongly disagree with the use of the word "large". The presented work is not a large study. Ten firearms were used in each of two studies (it's not clear if both datasets used the same 10 firearms). A large study would include at least 100 different firearms and even 100 is not likely to provide statistical confidence. This is a very important point. If the paper is allowed to state that the described work is a large study it will set a precedent that will be detrimental to the field.

### 2018-08-19 doc/paper.Rmd
couple more comments

Technological advances, such as profilometers and confocal microscopy allow \gk{one} to measure 3D surfaces in a high-resolution digitized form. This technology has become more accessible over the last decade, and has made its way into topological images of ballistics evidence, such as bullet lands and breech faces \cite{DeKinder1, DeKinder2, Bachrach1, vorburger2016}.
\gk{small change}Digitized images of 3D surfaces, form the basis of statistical analysis of toolmarks. A statistical approach based on data  removes both subjectivity from the assessment and allows a quantification of error rates for both false positive and false negative identifications.

\hh{changed citation style}
Methods for matching \gk{striated} marks for a variety of tools have been studied in the literature (see \autoref{tab:toolmarks-ER} for an overview):  in \cite{manytoolmarks1} and \cite{chumbley} digitized screwdriver marks have been analyzed using a profilometer;  in \cite{manytoolmarks2} 3D marks from screwdriver, tongue and groove pliers captured using a confocal microscope have been investigated; digitized marks from slip-joint pliers generated by a surface profilometer  have been investigated in \cite{afte-chumbley}.

\gk{changed} These digitized markings allow the use of statistical methods to quantify the scientific mechanism of comparing markings and serve as basis for an error rate calculation.
In \cite{manytoolmarks2} a relative distance metric is defined and used as similarity measure between two toolmarks. This approach is expanded in \citet{manytoolmarks1}: a set of small segments in the markings of two toolmarks are extracted and  similarity is compared using a maximum Pearson correlation coefficient. 
The Chumbley scoring method, first introduced in \cite{chumbley}, uses a similar but more extensive framework based on a Mann-Whitney U test of the resulting correlation coefficients. This approach is non-deterministic, because segments are chosen randomly.  In \cite{hadler}  the score is fixed to be deterministic for each pair of toolmarks by choosing segments for comparison systematically. This approach also ensures independence between segments of striae.

\begin{table}[ht]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{rlrrr}
  \hline
Research paper & Method & Data Source & False Positives & False Negatives\\
  \hline
 \textbf{Faden et al. (2007)} \cite{manytoolmarks1} & Maximum Pearson & Screwdrivers & & \\ & Correlation &  & - & - \\ \hline
 \textbf{Chumbley et al. (2010)} \cite{chumbley} & Randomized & Screwdrivers & & \\ (Same-Surface Same-Angle) & Chumbley Score & & 2.3\% & 8.9\%  \\ \hline
  \textbf{Grieve et al. (2014)}
 \cite{afte-chumbley} & Randomized & Slip-joint  &  & \\ & Chumbley Score &  & - & - \\ \hline 
  \textbf{Hadler \& Morris (2017)} \cite{hadler} & Deterministic & Screwdrivers & & \\ (Same-Surface Same-Angle) & Chumbley Score & & 0\% & 6\%  \\ \hline
  \textbf{Bachrach et al. (2010)} \cite{manytoolmarks2} & Similarity Measure & Screwdrivers & & \\ (Different Surfaces-same angle) & Relative Distance Metric & & 5.9\% &  9.4\% \\ (Same Surfaces-same angle)&  & & 0.22\% &  0\% \\
   \hline
\end{tabular}}
\caption{\label{tab:toolmarks-ER} Error Rates in same-source \gk{striated} toolmark analysis reported in the literature. The top four reported papers use some variation of the Chumbley-score method.}
\end{table}

@@

\begin{table}[ht]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{rlrrr}
  \hline
Method & Data Source & False Positives & False Negatives\\
  \hline
  \textbf{\citet{aoas}} & Hamby 252 (NIST scans) \\
Consecutive Matching Bullets Striae (CMS) &   &  6.25\% &  33.85\% \\ 
Consecutive Non-matching Striae (CNMS)  &  &  6.26\% & 35.42\%  \\ 
Average Distance (D) &   &   6.25\% & 45.83\% \\ 
Cross-correlation Function (CCF) & &  6.25\% & 17.71\%  \\ 
Sum of Peaks (S) &  &  6.25\% &  18.23\% \\
   \hline
   \textbf{\citet{chu2013}} & Hamby 252 (NIST scans) \\
Consecutive Matching Bullets Striae (CMS) &  &  0\% &  52\% \\ 
   \hline
   \textbf{\citet{chu2010}} & \small{6 types of firearms, 2 types of ammunition} \\
   \textbf{\citet{ma2004}} & \small{NIST standard bullet SRM 8240} \\
Cross-Correlation Function (CCF) &   &  - &  - \\ 
    \hline
\end{tabular}}
\caption{\label{tab:bullets-ER} Error Rates in same-source single feature land-to-land analysis reported in the literature. \hh{Note that only error rates from the same data source can be compared directly between methods. Error rates from different sources are influenced by type of firearm and ammunition used.}}
\end{table}

@@

For both same- and different-shift pairs correlations between the  markings are calculated. 
The intuition here is that for two markings from the same-source the correlation for the in-phase sample should be high, while the correlations of the out-of-phase sample  provide a measure for the base-level correlation for non-matching marks of a given length $w_v$.
\hh{More specifically, the null hypothesis of the Chumbley score test is stated as **$H_o$: the markings come from two different sources**} with the alternative given as **$H_a$: the markings come from the same source**. A $p$-value for the Chumbley score test is } then computed as a Mann Whitney U statistic to compare between in-phase sample and out-of-phase sample. A low $p$-value is then interpreted as a rejection of the null hypothesis in favor of the alternative hypothesis of `same-source`.}

@@

Looking closer at \autoref{eq.start}, we see that by definition, some number of tests will fail to produce a result. \hh{Note that this problem is different from erroneous test results.} The problem of failed tests is first mentioned in \citet{afte-chumbley}. Unfortunately, the authors do not provide any percentage of how many tests failed for their data. 
The algorithm fails to produce for two reasons: either the number of eligible same-shift pairs is zero, or the number of different-shift pairs is zero.

@@

\hh{Performance of tests is measured with respect to the errors they make in situations where ground truth is known. We distinguish between two error rates: (1) false positive and (2) false negative rate.
*False positives* (or *false identifications*) are situations where the test indicates a match (i.e. the test falsely rejects) but the markings come from different sources. This is also known as a *Type I* error. 
*False negatives* (or *missed identifications*) are situations where the test fails to reject, i.e. the test indicates that the markings come from different sources, but in fact the markings come from the same source. This is a *Type II* error.}

\hh{Note that in all of the following land-to-land comparisons only lands are compared that are suitable for a comparison, i.e. a signature can be extracted from the scan. In particular, lands which exhibited tank rash  were removed from comparison \citep{aoas}.
}

Section \ref{appendix:appxfailed} in the Appendix discusses  various scenarios of failed tests.
\begin{figure}[hbtp]
\centering
\includegraphics[width=.7\textwidth]{images/sketch-diff-2.png}
\caption{\label{sketch-diff-2}Sketch of adjusted different-shift pairings. At most one of the same-shift pairings can not be matched with a different-shift pair under algorithm (CS2). }
\end{figure}

@@

\subsection{Scenarios of failed tests}
\label{appendix:appxfailed}
Figures \ref{same-shift-failure} and \ref{diff-shift-failure} show scenarios in which the deterministic Chumbley score can fail. 
In \autoref{same-shift-failure} both CS1 and CS2 fail, because the lag between optimal locations is so large that no same-shift pairs can be found once the signatures are aligned. These failures are inherent to the Chumbley Score and cannot be prevented.
\begin{figure}[hbtp]
\centering
\includegraphics[width=0.62\textwidth]{images/same-shift-failure.png}

\autoref{diff-shift-failure} shows two situations, in which CS1 fails to identify any different-shift pairings. This happens, when both relative locations are close to either end of the signature. CS2 can still be computed in this situation as long as there are at least two same-shift pairs identified.

@@

>>>>

Technological advances, such as profilometers and confocal microscopy, have made it possible to capture 3D surfaces in a high-resolution digitized form. This technology has become more accessible over the last decade, and has made its way into topological images of ballistics evidence, such as bullet lands and breech faces \cite{DeKinder1, DeKinder2, Bachrach1, vorburger2016}.
Digitized images of 3D surfaces form the basis of statistical analysis of toolmarks. Statistical approaches based on this data remove both subjectivity from the assessment and allow a quantification of error rates for  false positive and false negative identifications.

Methods for matching striated marks for a variety of tools have been studied in the literature (see \autoref{tab:toolmarks-ER} for an overview):  in \cite{manytoolmarks1} and \cite{chumbley} digitized screwdriver marks have been analyzed using a profilometer;  in \cite{manytoolmarks2} 3D marks from screwdriver, tongue and groove pliers captured using a confocal microscope have been investigated; digitized marks from slip-joint pliers generated by a surface profilometer  have been investigated in \cite{afte-chumbley}.

These digitized markings allow the use of statistical methods to quantify the scientific mechanism of comparing markings and serve as basis for an error rate calculation.
In \cite{manytoolmarks2} a relative distance metric is defined and used as similarity measure between two toolmarks. This approach is expanded in \citet{manytoolmarks1}: a set of small segments in the markings of two toolmarks are extracted and  similarity is compared using a maximum Pearson correlation coefficient. 
The Chumbley scoring method, first introduced in \cite{chumbley}, uses a similar but more extensive framework based on a Mann-Whitney U test of the resulting correlation coefficients. This approach is non-deterministic, because segments are chosen randomly.  In \cite{hadler}  the score is fixed to be deterministic for each pair of toolmarks by choosing segments for comparison systematically. This approach also ensures independence between segments of striae.

\begin{table}[ht]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{rlrrr}
  \hline
Research paper & Method & Data Source & False Positives & False Negatives\\
  \hline
 \textbf{Faden et al. (2007)} \cite{manytoolmarks1} & Maximum Pearson & Screwdrivers & & \\ & Correlation &  & - & - \\ \hline
 \textbf{Chumbley et al. (2010)} \cite{chumbley} & Randomized & Screwdrivers & & \\ (Same-Surface Same-Angle) & Chumbley Score & & 2.3\% & 8.9\%  \\ \hline
  \textbf{Grieve et al. (2014)}
 \cite{afte-chumbley} & Randomized & Slip-joint  &  & \\ & Chumbley Score &  & - & - \\ \hline 
  \textbf{Hadler \& Morris (2017)} \cite{hadler} & Deterministic & Screwdrivers & & \\ (Same-Surface Same-Angle) & Chumbley Score & & 0\% & 6\%  \\ \hline
  \textbf{Bachrach et al. (2010)} \cite{manytoolmarks2} & Similarity Measure & Screwdrivers & & \\ (Different Surfaces-same angle) & Relative Distance Metric & & 5.9\% &  9.4\% \\ (Same Surfaces-same angle)&  & & 0.22\% &  0\% \\
   \hline
\end{tabular}}
\caption{\label{tab:toolmarks-ER} Error Rates in same-source analyses for  striated toolmarks reported in the literature. The top four reported papers use some variation of the Chumbley score method.}
\end{table}

@@

\begin{table}[ht]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{rlrrr}
  \hline
Method & Data Source & False Positives & False Negatives\\
  \hline
  \textbf{\citet{aoas}} & Hamby 252 (NIST scans) \\
Consecutive Matching Bullets Striae (CMS) &   &  6.25\% &  33.85\% \\ 
Consecutive Non-matching Striae (CNMS)  &  &  6.26\% & 35.42\%  \\ 
Average Distance (D) &   &   6.25\% & 45.83\% \\ 
Cross-correlation Function (CCF) & &  6.25\% & 17.71\%  \\ 
Sum of Peaks (S) &  &  6.25\% &  18.23\% \\
   \hline
   \textbf{\citet{chu2013}} & Hamby 252 (NIST scans) \\
Consecutive Matching Bullets Striae (CMS) &  &  0\% &  52\% \\ 
   \hline
   \textbf{\citet{chu2010}} & \small{6 types of firearms, 2 types of ammunition} \\
   \textbf{\citet{ma2004}} & \small{NIST standard bullet SRM 8240} \\
Cross-Correlation Function (CCF) &   &  - &  - \\ 
    \hline
\end{tabular}}
\caption{\label{tab:bullets-ER} Error Rates in same-source single feature land-to-land analysis reported in the literature. Note that only error rates from the same data source can be compared directly between methods. Error rates from different sources are influenced by type of firearm and ammunition used.}
\end{table}

@@

For both same- and different-shift pairs correlations between the  markings are calculated. 
The intuition here is that for two markings from the same-source the correlation for the in-phase sample should be high, while the correlations of the out-of-phase sample  provide a measure for the base-level correlation for non-matching marks of a given length $w_v$.
More specifically, the null hypothesis of the Chumbley score test is stated as **$H_o$: the markings come from two different sources** with the alternative given as **$H_a$: the markings come from the same source**. A $p$-value for the Chumbley score test is  then computed as a Mann Whitney U statistic to compare between in-phase sample and out-of-phase sample. A low $p$-value is  interpreted as a rejection of the null hypothesis in favor of the alternative hypothesis of `same-source`.

@@

Looking closer at \autoref{eq.start}, we see that by definition, some number of tests will fail to produce a result. \hh{Note that this problem is different from erroneous test results.} The problem of failed tests is first mentioned in \citet{afte-chumbley}. Unfortunately, the authors do not provide any percentage of how many tests failed for their data. 
The algorithm fails to produce for two reasons: either the number of eligible same-shift pairs is zero, or the number of different-shift pairs is zero. Section \ref{appendix:appxfailed} in the Appendix discusses scenarios of failed tests in more detail.

@@

Performance of tests is measured with respect to the errors a test makes in situations where ground truth is known. We distinguish between two error rates: (1) false positive and (2) false negative rate.
*False positives* (or *false identifications*) are situations where the test indicates a match (i.e. the test falsely rejects) but the markings come from different sources. This is also known as a *Type I* error. 
*False negatives* (or *missed identifications*) are situations where the test fails to reject, i.e. the test indicates that the markings come from different sources, but in fact the markings come from the same source. This is a *Type II* error.
In both cases error rates are calculated as the ratio of the number of errors observed and the number of tests executed.

Note that in all of the following land-to-land comparisons only lands are compared that are suitable for a comparison, i.e. a signature can be extracted from the scan. In particular, lands which exhibited tank rash  were removed from comparison \citep{aoas}.

\begin{figure}[hbtp]
\centering
\includegraphics[width=.7\textwidth]{images/sketch-diff-2.png}
\caption{\label{sketch-diff-2}Sketch of adjusted different-shift pairings. At most one of the same-shift pairings can not be matched with a different-shift pair under algorithm (CS2). }
\end{figure}

@@

\subsection{Scenarios of failed tests}
\label{appendix:appxfailed}
Figures \ref{same-shift-failure} and \ref{diff-shift-failure} show scenarios in which the deterministic Chumbley score can fail. 
\autoref{diff-shift-failure} shows two situations, in which CS1 fails to identify any different-shift pairings. This happens, when both relative locations are close to either end of the signature. CS2 can still be computed in this situation as long as there are at least two same-shift pairs identified.

@@

In \autoref{same-shift-failure} both CS1 and CS2 fail, because the lag between optimal locations is so large that no same-shift pairs can be found once the signatures are aligned. These failures are inherent to the Chumbley Score and cannot be prevented.
\begin{figure}[hbtp]
\centering
\includegraphics[width=0.62\textwidth]{images/same-shift-failure.png}

### 2018-08-19 doc/paper.tex
couple more comments

Technological advances, such as profilometers and confocal microscopy
allow {\textcolor{blue}{one}} to measure 3D surfaces in a
high-resolution digitized form. This technology has become more
accessible over the last decade, and has made its way into topological
images of ballistics evidence, such as bullet lands and breech faces
\cite{DeKinder1, DeKinder2, Bachrach1, vorburger2016}.
{\textcolor{blue}{small change}}Digitized images of 3D surfaces, form
the basis of statistical analysis of toolmarks. A statistical approach
based on data removes both subjectivity from the assessment and allows a
quantification of error rates for both false positive and false negative
identifications.

{\textcolor{orange}{changed citation style}}

@@

\begin{table}[ht]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{rlrrr}
  \hline
Method & Data Source & False Positives & False Negatives\\
  \hline
  \textbf{\citet{aoas}} & Hamby 252 (NIST scans) \\
Consecutive Matching Bullets Striae (CMS) &   &  6.25\% &  33.85\% \\ 
Consecutive Non-matching Striae (CNMS)  &  &  6.26\% & 35.42\%  \\ 
Average Distance (D) & Winchester  &   6.25\% & 45.83\% \\ 
Cross-correlation Function (CCF) & &  6.25\% & 17.71\%  \\ 
Sum of Peaks (S) &  &  6.25\% &  18.23\% \\
   \hline
   \textbf{\citet{chu2013}} & Hamby 252 (NIST scans) \\
Consecutive Matching Bullets Striae (CMS) &  &  0\% &  52\% \\ 
   \hline
   \textbf{\citet{chu2010}} & \small{6 types of firearms, 2 types of ammunition} \\
   \textbf{\citet{ma2004}} & \small{NIST standard bullet SRM 8240} \\
Cross-Correlation Function (CCF) &   &  - &  - \\ 
    \hline
\end{tabular}}
\caption{\label{tab:bullets-ER} Error Rates in same-source single feature land-to-land analysis reported in the literature. {\textcolor{blue}{Note that differences in error rates do not only come from different methods but also differently marking firearms and types of ammunition}}}
\end{table}

@@

For both same- and different-shift pairs correlations between the
markings are calculated. The intuition here is that for two markings
from the same-source the correlation for the in-phase sample should be
high, while the correlations of the out-of-phase sample provide a
measure for the base-level correlation for non-matching marks of a given
length \(w_v\). The Chumbley score is then computed as a Mann Whitney U
statistic to compare between in-phase sample and out-of-phase sample. In
the original method proposed in \citet{chumbley} both in-phase and
out-of-phase sample are extracted randomly, whereas \citet{hadler}
proposed the above specified deterministic rules for both samples to
make the resulting score deterministic while simultaneously avoiding
overlaps within selected marks to ensure independence.

@@

Looking closer at \autoref{eq.start}, we see that by definition, some
number of tests will fail to produce a result. The problem of failed
tests is first mentioned in \citet{afte-chumbley}. Unfortunately, the
authors do not provide any percentage of how many tests failed for their
data. The algorithm fails to produce for two reasons: either the number
of eligible same-shift pairs is zero, or the number of different-shift
pairs is zero.

@@

We then define the pairs for different-shifts as
\begin{equation}\label{eq.diff2}
\left(s_{(j)}^{(1)}, s_{(I-j+1)}^{(1)} \right) \text{ for } j = 
\begin{cases}
1, ..., I & \text{ for even } I \\
1, ..., (I-1)/2, (I-1)/2 + 2, ..., I & \text{ for odd } I
\end{cases},
\end{equation} i.e.~for an odd number of same-shift correlations, we
skip the middle pair for the different-shift correlations (see
\autoref{sketch-diff-2}). This pairing ensures that the number of
different-shift pairings is the same or at most one less than the number
of same-shift pairings in all tests. In the remainder of the paper, we
will refer to the algorithm defined by \citet{hadler} as \textbf{(CS1)}
and the suggested modified algorithm as \textbf{(CS2)} and compare their
performance on the available scans of the Hamby study. The section
\ref{appendix:appxfailed} of the Appendix discusses about the various
scenarious of failed tests.

@@

>>>>

Technological advances, such as profilometers and confocal microscopy,
have made it possible to capture 3D surfaces in a high-resolution
digitized form. This technology has become more accessible over the last
decade, and has made its way into topological images of ballistics
evidence, such as bullet lands and breech faces
\cite{DeKinder1, DeKinder2, Bachrach1, vorburger2016}. Digitized images
of 3D surfaces form the basis of statistical analysis of toolmarks.
Statistical approaches based on this data remove both subjectivity from
the assessment and allow a quantification of error rates for false
positive and false negative identifications.

@@

\begin{table}[ht]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{rlrrr}
  \hline
Method & Data Source & False Positives & False Negatives\\
  \hline
  \textbf{\citet{aoas}} & Hamby 252 (NIST scans) \\
Consecutive Matching Bullets Striae (CMS) &   &  6.25\% &  33.85\% \\ 
Consecutive Non-matching Striae (CNMS)  &  &  6.26\% & 35.42\%  \\ 
Average Distance (D) &   &   6.25\% & 45.83\% \\ 
Cross-correlation Function (CCF) & &  6.25\% & 17.71\%  \\ 
Sum of Peaks (S) &  &  6.25\% &  18.23\% \\
   \hline
   \textbf{\citet{chu2013}} & Hamby 252 (NIST scans) \\
Consecutive Matching Bullets Striae (CMS) &  &  0\% &  52\% \\ 
   \hline
   \textbf{\citet{chu2010}} & \small{6 types of firearms, 2 types of ammunition} \\
   \textbf{\citet{ma2004}} & \small{NIST standard bullet SRM 8240} \\
Cross-Correlation Function (CCF) &   &  - &  - \\ 
    \hline
\end{tabular}}
\caption{\label{tab:bullets-ER} Error Rates in same-source single feature land-to-land analysis reported in the literature. Note that only error rates from the same data source can be compared directly between methods. Error rates from different sources are influenced by type of firearm and ammunition used.}
\end{table}

@@

For both same- and different-shift pairs correlations between the
markings are calculated. The intuition here is that for two markings
from the same-source the correlation for the in-phase sample should be
high, while the correlations of the out-of-phase sample provide a
measure for the base-level correlation for non-matching marks of a given
length \(w_v\). More specifically, the null hypothesis of the Chumbley
score test is stated as \textbf{\(H_o\): the markings come from two
different sources} with the alternative given as \textbf{\(H_a\): the
markings come from the same source}. A \(p\)-value for the Chumbley
score test is then computed as a Mann Whitney U statistic to compare
between in-phase sample and out-of-phase sample. A low \(p\)-value is
interpreted as a rejection of the null hypothesis in favor of the
alternative hypothesis of \texttt{same-source}.

In the original method proposed in \citet{chumbley} both in-phase and
out-of-phase sample are extracted randomly, whereas \citet{hadler}
proposed the above specified deterministic rules for both samples to
make the resulting score deterministic while simultaneously avoiding
overlaps within selected marks to ensure independence.

@@

Looking closer at \autoref{eq.start}, we see that by definition, some
number of tests will fail to produce a result.
{\textcolor{orange}{Note that this problem is different from erroneous test results.}}
The problem of failed tests is first mentioned in \citet{afte-chumbley}.
Unfortunately, the authors do not provide any percentage of how many
tests failed for their data. The algorithm fails to produce for two
reasons: either the number of eligible same-shift pairs is zero, or the
number of different-shift pairs is zero. Section
\ref{appendix:appxfailed} in the Appendix discusses scenarios of failed
tests in more detail.

@@

We then define the pairs for different-shifts as
\begin{equation}\label{eq.diff2}
\left(s_{(j)}^{(1)}, s_{(I-j+1)}^{(1)} \right) \text{ for } j = 
\begin{cases}
1, ..., I & \text{ for even } I \\
1, ..., (I-1)/2, (I-1)/2 + 2, ..., I & \text{ for odd } I
\end{cases},
\end{equation} i.e.~for an odd number of same-shift correlations, we
skip the middle pair for the different-shift correlations (see
\autoref{sketch-diff-2}). This pairing ensures that the number of
different-shift pairings is the same or at most one less than the number
of same-shift pairings in all tests. In the remainder of the paper, we
will refer to the algorithm defined by \citet{hadler} as \textbf{(CS1)}
and the suggested modified algorithm as \textbf{(CS2)} and compare their
performance on the available scans of the Hamby study.

Performance of tests is measured with respect to the errors a test makes
in situations where ground truth is known. We distinguish between two
error rates: (1) false positive and (2) false negative rate. \emph{False
positives} (or \emph{false identifications}) are situations where the
test indicates a match (i.e.~the test falsely rejects) but the markings
come from different sources. This is also known as a \emph{Type I}
error. \emph{False negatives} (or \emph{missed identifications}) are
situations where the test fails to reject, i.e.~the test indicates that
the markings come from different sources, but in fact the markings come
from the same source. This is a \emph{Type II} error. In both cases
error rates are calculated as the ratio of the number of errors observed
and the number of tests executed.

Note that in all of the following land-to-land comparisons only lands
are compared that are suitable for a comparison, i.e.~a signature can be
extracted from the scan. In particular, lands which exhibited tank rash
were removed from comparison \citep{aoas}.

@@

\begin{table}[hbtp]
\centering
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{rrrlrrl}
  \hline
  & \multicolumn{3}{l}{\bf CS1} & \multicolumn{3}{l}{\bf CS2} \\
$w_o$ & \bf FPR & \bf FNR & \bf AUC (95\% C.I.) & \bf FPR & \bf FNR & \bf AUC (95\% C.I.) \\  
  \hline
%90 & 0.077 & 0.546 & 0.680 (0.633, 0.727) & 0.056 & 0.478 & 0.729 (0.684, 0.774) \\
%  120 & 0.082 & 0.485 & 0.736 (0.693, 0.779) & 0.056 & 0.452 & 0.763 (0.720, 0.806) \\
%  150 & 0.080 & 0.493 & 0.730 (0.685, 0.775) & 0.055 & 0.422 & 0.774 (0.733, 0.816) \\
%  180 & 0.087 & 0.458 & 0.773 (0.734, 0.813) & 0.055 & 0.435 & 0.773 (0.730, 0.816) \\
  210 & 0.086 & 0.413 & 0.780 (0.740, 0.821) & 0.055 & 0.387 & 0.803 (0.763, 0.843) \\ 
  240 & 0.085 & 0.427 & 0.784 (0.744, 0.824) & 0.055 & 0.365 & 0.801 (0.760, 0.841) \\ 
  270 & 0.082 & 0.415 & 0.782 (0.741, 0.823) & 0.048 & 0.374 & 0.808 (0.769, 0.848) \\ 
  300 & 0.082 & 0.405 & 0.791 (0.751, 0.832) & 0.051 & 0.383 & 0.814 (0.776, 0.852) \\ 
  330 & 0.082 & 0.428 & 0.791 (0.753, 0.830) & 0.050 & 0.383 & 0.804 (0.765, 0.844) \\ 
  360 & 0.083 & 0.427 & 0.788 (0.747, 0.828) & 0.049 & 0.400 & 0.803 (0.765, 0.842) \\ 
  390 & 0.085 & 0.400 & 0.789 (0.748, 0.830) & 0.050 & 0.383 & 0.810 (0.771, 0.849) \\ 
   \hline
\end{tabular}
\end{adjustbox}
\caption{\label{tab:aucsh44} Overview of high resolution scan results as shown in Figures \ref{fig:h44}. FPR is the observed rate of false positives (for a fixed level $\alpha = 0.05$), FNR is the false negative rate. Area under the curve (AUC) is shown with 95\% confidence intervals. }
\end{table}
